\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{enumitem}
%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge Mahdi \textsc{Barzegar Khalilsarai}
	}\bigskip\par}

%--------------------SECTIONS-----------------------------------
\section{Personal Data}

\begin{tabular}{ll}
   \textsc{Tel:}     & +49(0)3031429548\\
%   \textsc{Mobile:}     & +49(0)17629872624\\
   \textsc{email:}     & \href{m.barzegarkhalilsarai@tu-berlin.de}{m.barzegarkhalilsarai@tu-berlin.de}\\
   \textsc{Website:}     & \href{https://mbarzegar.github.io/}{www.mbarzegar.github.io}\\
%   \textsc{Address:}     & Mollwitzstrasse 4, 14059, Berlin, Germany
\end{tabular}


\section{Research Interests}
\begin{itemize}
 \item Signal Processing
\item Convex Optimization
\item Machine Learning
\item Wireless Communication and Massive MIMO Systems
\end{itemize}


%Section: Education
\section{Education}
\begin{tabular}{rl}	
\textsc{Present} &PhD candidate in \textsc{ Communication Systems}\\
\textsc{Summer 2016} & \textbf{Department of Telecommunication Systems, }\\
~ & \textbf{Technische Universit\"{a}t Berlin},  Berlin, Germany\\
&  Advisors: Prof. Giuseppe \textsc{Caire} and Prof. Gerhard \textsc{Wunder}\\	
& \textbf{Graduation Date: 01.01.2021 (expected)}\vspace{3mm}\\
	
\textsc{Spring} 2015 & M.Sc. in \textsc{ Communication Systems}\\
\textsc{Fall 2013} & \textbf{EE School, Sharif University of Technology}, Tehran, Iran\\
& \textbf{Thesis:} ``Statistical Interpolation of Non-Gaussian AR Processes" \\
&  Advisor: Prof. Arash \textsc{Amini}\\
&\normalsize \textsc{Gpa}: 17.64/20\vspace{3mm}\\



\textsc{Spring} 2013& B.Sc. in \textsc{Electrical Engineering} \\
\textsc{Fall} 2009 & \textbf{ECE School, University of Tehran}, Tehran, Iran\\ 
%& \textbf{Thesis:} ``Analysis, Design and Implementation of a Phased Array Antenna\\
%& \hspace{12.5 mm} System Concerning Low Earth Orbit (LEO) satellite communications''\\
%& Advisor:  Prof. Ali-Azam \textsc{Abbasfar}\\
&\normalsize \textsc{Gpa}: 17.14/20\\


%\textsc{Spring} 2009& Pre-University Cerificate in \textsc{Mathematics \& Physics}\\
%\textsc{Fall} 2008& Shahid Panaahi Pre-University Center, Alborz, Iran\\
%&\textsc{Gpa}: 19.68/20 \\\\
%
%\textsc{Spring} 2008& High School Diploma in \textsc{Mathematics \& Physics}\\
%\textsc{Fall} 2005& Shahid Rajaee High School, Alborz, Iran\\
%&\textsc{Gpa}: 19.28/20 \\\\

\end{tabular}


%Section: Honors
\section{Honors}
\begin{tabular}{rl}	
 \textsc{2013}  & Nationwide University Entrance Exam in Electrical Engineering for Graduate Studies, Iran.\\
& Rank: \textbf{31} (among about \textbf{10,000} participants)\\\\

\textsc{2009}& Nationwide University Entrance Exam in Mathematics \& Physics, Iran. \\
& Rank: \textbf{279} (among about \textbf{308,000} participants)\\\\

\textsc{2009}& Nationwide University Entrance Exam in Foreign Languages, Iran.\\
& Rank: \textbf{4} (among about \textbf{126,000} participants)\\\\

\end{tabular}



%Section: TA
\section{Teaching Assistance}
\begin{tabular}{ll}	
 \textsc{Spring 2014}  & \textbf{Signals \& Systems}\\
\textsc{Fall 2013}& \textbf{Signals \& Systems} \\
\vspace{1mm}
\textsc{Spring 2011}& \textbf{Mathematics II}\\
\end{tabular}


%Section: Publications
\newpage
\section{Research Papers}
\begin{enumerate}
	\subsection*{Published}
	% first author
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Saeid Haghighatshoar, and Giuseppe Caire. ``Joint Approximate Covariance Diagonalization with Applications in MIMO Virtual Beam Design." proceedings of the IEEE Global Communications Conference (Globecom), 2020.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Benedikt Gross, Stelios Stefanatos, Gerhard Wunder, Giuseppe Caire. ``WiFi-Based Channel Impulse Response Estimation and Localization via Multi-Band Splicing." proceedings of the IEEE Global Communications Conference (Globecom), 2020.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Tianyu Yang, Saeid Haghighatshoar, and Giuseppe Caire. ``Structured Channel Covariance Estimation for Dual-Polarized Massive MIMO Arrays." In WSA 2020; 24th International ITG Workshop on Smart Antennas, pp. 1-6. VDE, 2020.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Tianyu Yang, Saeid Haghighatshoar, Xinping Yi, and Giuseppe Caire. ``Active Channel Sparsification and Precoding for Dual-Polarized FDD Massive MIMO." In WSA 2020; 24th International ITG Workshop on Smart Antennas, pp. 1-6. VDE, 2020.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Tianyu Yang, Saeid Haghighatshoar, and Giuseppe Caire. ``Structured channel covariance estimation from limited samples in massive MIMO." In ICC 2020-2020 IEEE International Conference on Communications (ICC), pp. 1-7. IEEE, 2020.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Stelios Stefanatos, Gerhard Wunder, and Giuseppe Caire. ``WiFi-based indoor localization via multi-band splicing and phase retrieval." In 2019 IEEE 20th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC), pp. 1-5. IEEE, 2019.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Yi Song, Tianyu Yang, Saeid Haghighatshoar, and Giuseppe Caire. ``Uplink-Downlink Channel Covariance Transformations and Precoding Design for FDD Massive MIMO." In 2019 53rd Asilomar Conference on Signals, Systems, and Computers, pp. 199-206. IEEE, 2019.
	w	 	 	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Saeid Haghighatshoar, Xinping Yi, and Giuseppe Caire. ``FDD massive MIMO via UL/DL channel covariance extrapolation and active channel sparsification." IEEE Transactions on Wireless Communications 18, no. 1 (2018): 121-135.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Saeid Haghighatshoar, and Giuseppe Caire. ``How to achieve massive MIMO gains in FDD systems?." In 2018 IEEE 19th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC), pp. 1-5. IEEE, 2018.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Saeid Haghighatshoar, Xinping Yi, and Giuseppe Caire. ``FDD massive MIMO: Efficient downlink probing and uplink feedback via active channel sparsification." In 2018 IEEE International Conference on Communications (ICC), pp. 1-6. IEEE, 2018.
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Saeid Haghighatshoar, Giuseppe Caire, and Gerhard Wunder. ``Compressive estimation of a stochastic process with unknown autocorrelation function." In 2017 IEEE International Symposium on Information Theory (ISIT), pp. 1282-1286. IEEE, 2017.
	
	% Collaborator
	\item Song, Yi, \textbf{Mahdi Barzegar Khalilsarai}, Saeid Haghighatshoar, and Giuseppe Caire. ``Machine Learning for Geometrically-Consistent Angular Spread Function Estimation in Massive MIMO." arXiv preprint arXiv:1910.13795 (2019).
	
	\item Haghighatshoar, Saeid, \textbf{Mahdi Barzegar Khalilsarai}, and Giuseppe Caire. ``Multi-band covariance interpolation with applications in massive MIMO." In 2018 IEEE International Symposium on Information Theory (ISIT), pp. 386-390. IEEE, 2018.
	
	\item Wunder, Gerhard, Ingo Roth, \textbf{Mahdi Barzegar Khalilsarai}, Axel Flinth, Saeid Haghighatshoar, Giuseppe Caire, and Gitta Kutyniok. "Hierarchical sparse channel estimation for massive MIMO." In WSA 2018; 22nd International ITG Workshop on Smart Antennas, pp. 1-8. VDE, 2018.
	
	\item Stefanatos, Stelios, \textbf{Mahdi Barzegar Khalilsarai}, and Gerhard Wunder. ``Wideband massive MIMO channel estimation via sequential atomic norm minimization." In 2018 IEEE Global Conference on Signal and Information Processing (GlobalSIP), pp. 998-1002. IEEE, 2018.
	
	\item Tian, Chang, An Liu, \textbf{Mahdi Barzegar Khalilsarai}, Giuseppe Caire, Wu Luo, and Min-Jian Zhao. ``Randomized Channel Sparsifying Hybrid Precoding for FDD Massive MIMO Systems." IEEE Transactions on Wireless Communications (2020).
	%	 	 \end{enumerate}
	\noindent\subsection*{Under Review and ArXiv Preprints}
	%	 \subsection*{Under Review and ArXiv Preprints}
	%	 \begin{enumerate}
	\item  \textbf{Barzegar Khalilsarai, Mahdi}, Tianyu Yang, Saeid Haghighatshoar, Xinping Yi, and Giuseppe Caire. ``Dual-Polarized FDD Massive MIMO: A Comprehensive Framework." under review at the IEEE Transactions on Wireless Communications (TWC), arXiv preprint arXiv:\\2008.11182 (2020).
	
	\item \textbf{Barzegar Khalilsarai, Mahdi}, Guiseppe Caire, Axel Flinth, Saeid Haghighatshoar, Gitta Kutyniok, and Gerhard Wunder. (alphabetic order) ``Estimation of Angles of Arrival Through Superresolution--A Soft Recovery Approach for General Antenna Geometries." arXiv preprint arXiv:1711.03996 (2017).
	
%	\item  Yi Song, \textbf{Mahdi Barzegar Khalilsarai}, Saeid Haghighatshoar, and Giuseppe Caire. ``Angular Power Spectrum Estimation in Massive MIMO using Deep Neural Networks." under review at the IEEE Transactions on Wireless Communications (TWC), 2020.
%	
%	\item  Tianyu Yang, \textbf{Mahdi Barzegar Khalilsarai}, Saeid Haghighatshoar, Xinping Yi, and Giuseppe Caire. ``Structured Channel Covariance Estimation from Limited Samples in Massive MIMO." under review at the IEEE Transactions on Wireless Communications (TWC), 2020.
\end{enumerate}
%Section: Graduate Courses
\section{Selected Courses}
\begin{tabular}{ll}	
\vspace{2 mm}
 \textsc{Stochastic Processes}  & \textsc{Time-Frequency Analysis} \\
\vspace{2 mm}
 \textsc{Information Theory}  &\textsc{Data Compression} \\
\vspace{2 mm}
 \textsc{Advanced Digital Communications}  & \textsc{Compressive Sensing} \\
\vspace{2 mm}
\textsc{Machine Learning} & \textsc{Functional Analysis}  \\

\end{tabular}

\section{Academic Service}
\textbf{Journal and Conference Review}\\
IEEE Trans. on Communications\\
  IEEE Communications Letters\\
  IEEE Signal Processing Letters \\
  IEEE International Symposium on Information theory (ISIT)\\
  IEEE Global Communications Conference (Globecom)\\
  IEEE Wireless Communications and Networking Conference (WCNC)\\
  IEEE International Conference on Communications (ICC)\\



%Section: R & L
%\section{Research \& Lab Experience}
%\begin{tabular}{rl}	
%\textsc{Spring 2013}& \textbf{Wireless Multimedia Communications Course Lab}\\
%& \textbf{Final Project:} Image Compression Using Transform Coding \\
%\vspace{3 mm}
%& \footnotesize{(Software Design Using MATLAB and Hardware Implementation by TMS320C6713 DSP Starter Kit)}\\
%\textsc{Spring 2013}& \textbf{Digital Signal Processing Course Lab   } \\
%& \textbf{Final Project:} Speech Watermarking using Adaptive Vector Quantization  \\
%& \hspace{21.5 mm} Index Modulation \\
%\vspace{3 mm}
%& \footnotesize{(Software Design Using MATLAB and Hardware Implementation by TMS320C6713 DSP Starter Kit)}\\
% \textsc{Spring 2012}  & \textbf{Digital Signal Processing Course}\\
%& \textbf{Final Project:} Speech Analysis and Synthesis Using Harmonic Models \\
%& \footnotesize{(Software Design by MATLAB)}\\
%
%\end{tabular}

%Section: E P 
%\section{Extra Projects}
%\begin{tabular}{rl}	
%\textsc{Summer 2014}& \textbf{Acoustic Vehicle Detection}\\ 
%& Capturing Environmental Sounds and Detecting the Presence of any\\
%\vspace{3 mm}
%& Kind of Motor Vehicles Using a PCA-Based Approach \\
%\textsc{Fall 2013}& \textbf{Face Image Segmentation } \\
%& Detecting Facial Components in an Image Using Viola-Jones Algorithm \\
%\end{tabular}


%Section: Tech Skills 
\section{Technical Skills}
\begin{tabular}{rl}	
\vspace{2 mm}
\textbf{Programming Languages} & MATLAB \& Simulink, Python, {\fb \LaTeX}  \\ 
\end{tabular}


%Section: Languages
\section{Languages}
\begin{tabular}{rl}
\vspace{1 mm}
 \textsc{Persian}&Mothertongue\\
\textsc{English}&Fluent\\
& \textbf{TOEFL (iBT):} 112/120 (Reading: 30/30, Listening: 27/30, Speaking: 27/30, Writing: 28/30)\\
\vspace{1 mm}
& \textbf{GRE:}  Verbal: 160/170, Quantitative: 164/170, Writing: 4/6 \\
\textsc{German}&Intermediate (Level B1)\\
\end{tabular}

\section{References}
\begin{enumerate}
	\item Giuseppe Caire, Professor, Institute for Telecommunication Systems, Technical University of Berlin, Berlin, Germany.\\
	\textit{email:} {\sf caire[AT]tu-berlin.de}, \hspace{26mm} \textit{Tel:} +49(0)30 314-29668.
	\item Gerhard Wunder, Professor, Department of Mathematics and Computer Science, Free University of Berlin, Berlin, Germany.\\
	\textit{email:} {\sf g.wunder[AT]fu-berlin.de}, \hspace{20mm} \textit{Tel:} +49(0)30 838-61931.	
	\item Dr. Saeid Haghighatshoar, Institute for Telecommunication Systems, Technical University of Berlin, Berlin, Germany.\\
	\textit{email:} {\sf saeid.haghighatshoar[AT]tu-berlin.de}, \hspace{3mm} \textit{Tel:} +49(0)30 314-28461.	
	\item  Dr. Xinping Yi, Department of Electrical Engineering and Electronics, University of Liverpool, Liverpool, United Kingdom.\\
	\textit{email:} {\sf xinping.yi [AT]liv.ac.uk}, \hspace{22mm} \textit{Tel:} +44 (0)151 795 9753.	
	\item Arash Amini, Professor, Department of Engineering, Sharif University of Technology, Tehran, Iran.\\
	\textit{email:} {\sf aamini[AT]sharif.ir}, \hspace{29mm} \textit{Tel:} +98(0)21 6616-4382.	
\end{enumerate}
%\section{Interests \& Hobbies}
%%\begin{tabular}{rl}
%%\end{tabular}
%
%\begin{itemize}[leftmargin=*]
%\item  Reading Books (esp. on Topics Concerning Philosophy)
%\item Playing Chess (Received a Silver Medal on Helaal-Ahmar Nationwide Team Competitions)
%\item Listening Music
%\end{itemize}

%\section{References}
%\begin{itemize}
%\item \textbf{Dr.Arash Amini} \\
%Dept. of Electrical Engineering, Sharif University of Technology, Tehran, Iran\\
%\textsc{email:} \href{aamini@ee.sharif.edu}{aamini@ee.sharif.edu}
%
%\item \textbf{Prof. Farrokh Marvasti} \\
%Dept. of Electrical Engineering, Sharif University of Technology, Tehran, Iran\\
%\textsc{email:} \href{marvasti@ee.sharif.edu}{marvasti@ee.sharif.edu}
%
%\item \textbf{Prof. Amir Masoud Rabiei} \\
%Dept. of Electrical \& Computer Engineering, University of Tehran, Tehran, Iran\\
%\textsc{email:} \href{rabiei@ut.ac.ir}{rabiei@ut.ac.ir}
%\end{itemize}

\end{document}
